\chapter{Appendix C. Questions asked after the fixed route trial and
proposal section}

\label{appc:afterquestions}

\section{After the bike ride}
\begin{enumerate}
\item Did everything work as expected?
\item Tell me the places that you felt danger.
\item For example, there two locations were the place it recently had accidents. 
\item Tell me the places that you felt safe.
\item Did the app make you more conscious about road safety? 
\section{Before showing the synthetic side}
\item Do you know the proper procedure to propose or send a petition if you want to change a portion of the city?
\section{After showing the synthetic side}
\item Did the app make you feel agency or your data represents what you want?
\item One thing we wanted to know about this experiment is about the procedure. It has two stages, the analytical and synthetic side. Did you feel your reporting and was it different when you were proposing. 
\item Do you see any advantages having the data collection visualization and proposals and voting in the same platform? What is different than having it separately?
\item Do you think the public will appreciate it and people will use this app in a real context?
\item I'm thinking there are two main ways to use this app. One situation
  is to have the city define a road to concentrate and have volunteers pass
  and put reports and improvement plans. The other is the unlimited, which
  citizen has full freedom to report and propose where ever they want.
\end{enumerate}
\clearpage
\newpage
